Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-07-13 nlp.tex
More writing

\subsection{Probabilistic Context-Free Grammar}
Pattern-recognition problems such as parsing date and time formats initiate from observations generated by some structured stochastic process. In other words, even if the initial higher-level production rule of the grammar is known (i.e. date, time or date-time), there could be several directions that the parser resolves to. For example, in a date string \texttt{5/6/2015}, the pattern could either be \texttt{M/d/yyyy} or \texttt{d/M/yyyy}.

@@

(add the rules for how probabilistic weights are assigned to the CFG)

>>>>

\subsection{Probabilistic Context-Free Grammar}

%Statistical parsing uses a probabilistic model of syntax in order to assign probabilities to each parse tree.
%Provides principled approach to resolving syntactic ambiguity.
%Allows supervised learning of parsers from tree-banks of parse trees provided by human linguists.
%Also allows unsupervised learning of parsers from corpora.

Pattern-recognition problems such as parsing date and time formats initiate from observations generated by some structured stochastic process. In other words, even if the initial higher-level production rule of the grammar is known (i.e. date, time or date-time), there could be several directions that the parser resolves to. For example, in a date string \texttt{5/6/2015}, the pattern could either be \texttt{M/d/yyyy} or \texttt{d/M/yyyy}.

@@

(add the rules for how probabilistic weights are assigned to the CFG)
(show cfg with prob values)
(examples -> one ambiguous, one not)
(parse tree with final probability weights)

\subsection{Training the PCFG}

(used a subset of the public data)

Having defined initial probabilistic weights to the CFG, we train the PCFG with a known training set of date time formats to enhance the coverage of the weights to the various production rules of the grammar.

\subsection{Parsing the PCFG}
Given a date-time string $s$, as input, we determine the highest scoring parse tree $t$ as  $max_{t \in T(s)} p(t)$.
